---
title: "Test01"
author: "Roberto Gainza"
date: "September 18, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  engine.path = list(octave = "C://myApps/Octave/octave-5.2.0/mingw64/bin/octave-cli.exe"))
```

## 

```{python}
import simpy
import numpy as np
m = 5
simpy.Environment()
print(np.abs(-6))
print(m)
```

```{octave}
# Here I have a problem, It doesn't recognize octave as a chunck
# I need to solve it.
z1 = complex(1, 2)
class(z1)
```

## Documentation to use the reticulate library. https://blog.rstudio.com/2018/03/26/reticulate-r-interface-to-python/



## In this chunck we use python code in a R chunck.
## We need the library reticulate to use python code.
```{r}
library(reticulate)
use_python("c://Users//MarcosRoberto///Anaconda3//python.exe")
os <- import("os")
os$listdir(".")
```

## In this chunk we use a python scritp inside a R chunck
```{r}
source_python("add.py")
add(3, 5)
```

## In a R chunck we work with python libraries and finaly we convert python objects in R objects
```{r}
np <- import("numpy", convert = FALSE)

x <- np$array(c(1:5))
sum <- x$cumsum()
print(sum)

py_to_r(sum)

```

## In this chunk we are going to view how to get help from python and R
```{r}
os <- import("os")
help("py_to_r")
py_help(os$chdir)
```



## Now I transfer data from R to python
```{r}
data <- iris
head(data)
data_py <- r_to_py(data)
```
```{python}
import numpy as np
import pandas as pd

r.data_py.head()
```

```{r}
library(reticulate)
reticulate::py_run_string("x = 10")
reticulate::py$x

reticulate::source_python("add.py")
reticulate::py$add(4, 5)
```
```{r}
mybuiltins <- reticulate::import_builtins()
mybuiltins$print("I love Elaheh")
```

